FoRTE baseline

### 2019-10-14 analysis/paper/paper.Rmd
Draft partial variance text

Except for the configurations with persistently low productivity, parameter uncertainty (across ensembles within each model configuration) was much larger than structural uncertainty (variance in ensemble means across configurations; Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question.
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) slightly reduced variability in primary productivity, slightly increased variability in Shannon diversity, and had mixed effects on aboveground biomass and total leaf area.
Enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) dramatically decreased variability in primary productivity and Shannon diversity and increased variability in leaf area, and had mixed effects on aboveground biomass.
reduced variance in aboveground biomass, diversity, and primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased variance in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on variance in productivity productivity.

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, eval = FALSE}
uncertainty_analysis_cap <- paste(
  htmlfig(),
  "Parameter sensitivity and uncertainty analysis, by model type,",
  "for 1975-2000 averaged growing season net primary productivity (left) and leaf area index (right).",
  "Elasticity (top) is the normalized sensitivity of the model to a fixed change in the parameter.",
  "Partial variance (bottom) describes the overall contribution of the parameter to model predictive uncertainty based on the combination of parameter uncertainty and model sensitivity.",
  "Each panel shows the top 10 parameter values, in terms of the absolute value of the corresponding quantity.",
  "Input parameter distributions are shown in Figure 1.",
  "Note that x-axis scales vary across panels."
)
readd(sensitivity_plot_knit)
```

Model sensitivity to specific parameters ["elasticity" _sensu_ @lebauer_2013_facilitating] varied depending on the model configuration and the target output variable (Figure 5).
The parameter with the single highest elasticity to NPP and LAI across all model configurations was specific leaf area (SLA), though the PFT whose SLA was most important varied with model configuration.
Other frequently (but not always) important parameters were the leaf C:N ratio (`c2n_leaf`), ratio of fine root to leaf biomass (`fineroot2leaf`), leaf and root respiration rates, and leaf optical properties (`leaf_reflect_vis/nir`).
<!-- TODO Dig into model configurations. -->

The parameters that contributed most to overall model predictive uncertainty ("partial variance") differed from parameters to which the model was most sensitive (Figure 5), largely driven by the fact that many of the parameters with the highest sensitivity (e.g. SLA, V~cmax~) were also well constrained by data (Figure 1).
Leaf optical properties of at least one PFT were among the top 10 most important parameters across all configurations, and in multiple cases, were the most important.
Other often important parameters were plant-soil water conductance (`water_conductance`), parameters related to adult mortality (`mort1,2,3`), and growth respiration.
Again, patterns in partial variance were largely idiosyncratic across model configurations.
<!-- TODO Dig into this more -->
<!-- TODO Check this analysis. Look at pairs plots of trait vs. variable, and my SA spline fits. -->

>>>>

<!--
Except for the configurations with persistently low productivity, parameter uncertainty (across ensembles within each model configuration) was much larger than structural uncertainty (variance in ensemble means across configurations; Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question.
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) slightly reduced variability in primary productivity, slightly increased variability in Shannon diversity, and had mixed effects on aboveground biomass and total leaf area.
Enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) dramatically decreased variability in primary productivity and Shannon diversity and increased variability in leaf area, and had mixed effects on aboveground biomass.
reduced variance in aboveground biomass, diversity, and primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased variance in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on variance in productivity productivity.
-->

```{r partial-variance-npp, fig.cap = partial_variance_npp_cap}
partial_variance_npp_cap <- paste(
  htmlfig(),
  "Contributions of individual parameters to predicted uncertainty in NPP,",
  "by model type.",
  "Panels on the left are for the \"peak\" NPP period (averaged over 1925-1950),",
  "and on the right are for the end of the simulation (averaged over 1975-1999)",
  "Each panel shows the top 8 parameter values in terms of their variance contribution.",
  "Input parameter distributions are shown in Figure 1.",
  "Note that x-axis scales vary across panels."
)
fig("partial-variance-npp.png")
```

```{r partial-variance-lai, fig.cap = partial_variance_lai_cap}
partial_variance_lai_cap <- paste(
  htmlfig(),
  "Same as above, but for total leaf area index (LAI)."
)
fig("partial-variance-lai.png")
```

<!-- Model sensitivity to specific parameters ["elasticity" _sensu_ @lebauer_2013_facilitating] varied depending on the model configuration and the target output variable (Figure 5). -->
<!-- The parameter with the single highest elasticity to NPP and LAI across all model configurations was specific leaf area (SLA), though the PFT whose SLA was most important varied with model configuration. -->
<!-- Other frequently (but not always) important parameters were the leaf C:N ratio (`c2n_leaf`), ratio of fine root to leaf biomass (`fineroot2leaf`), leaf and root respiration rates, and leaf optical properties (`leaf_reflect_vis/nir`). -->
<!-- TODO Dig into model configurations. -->

The parameters that contributed most to overall model predictive uncertainty ("partial variance") varied with model structure, time period considered, and output variable (NPP or LAI).
In general, uncertainties in pine growth respiration factor and early hardwood plant-soil water conductance contributed the most to parameter uncertainty in NPP during the "peak" period (1925-1950).
{TODO: Fill in the rest of this text...}

<!-- This is old text... -->
<!-- ...differed from parameters to which the model was most sensitive (Figure 5), largely driven by the fact that many of the parameters with the highest sensitivity (e.g. SLA, V~cmax~) were also well constrained by data (Figure 1). -->
<!-- Leaf optical properties of at least one PFT were among the top 10 most important parameters across all configurations, and in multiple cases, were the most important. -->
<!-- Other often important parameters were plant-soil water conductance (`water_conductance`), parameters related to adult mortality (`mort1,2,3`), and growth respiration. -->
<!-- Again, patterns in partial variance were largely idiosyncratic across model configurations. -->
<!-- TODO Dig into this more -->
<!-- TODO Check this analysis. Look at pairs plots of trait vs. variable, and my SA spline fits. -->

{TODO: Basic analysis of contributions from parameter interactions, a la Raczka et al. 2018? I expect these will be important.}
